Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-10-10 paper/main.tex
incorporated feedback from @morriscb
auncomment line on internal review and add names

%This paper has undergone internal review in the LSST Dark Energy Science Collaboration. % REQUIRED if true

@@

The authors would like to thank their LSST-DESC publication review committee for comments that improved the paper draft.

{ \red{personal funding sources}}
S.~Schmidt acknowledges support from DOE grant DE-SC0009999 and NSF/AURA grant N56981C.
AIM acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research.
During the completion of this work, AIM was advised by David W. Hogg and was supported by National Science Foundation grant AST-1517237.

>>>>

This paper has undergone internal review in the LSST Dark Energy Science Collaboration, the internal reviewers were: Daniel Gruen, Markus Rau, and Michael Troxel. % REQUIRED if true

@@

The authors would like to thank their LSST-DESC publication review committee for comments that improved the paper draft.
% hack event acknowledgments are important
%We thank Stony Brook University for hosting the Summer 2017 LSST-DESC Hack Day at which this work was partially completed.

{ \red{personal funding sources}}
SJS acknowledges support from DOE grant DE-SC0009999 and NSF/AURA grant N56981C.
AIM acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research.
During the completion of this work, AIM was advised by David W. Hogg and was supported by National Science Foundation grant AST-1517237.
%JYHS is advised by Ofer Lahav and acknowledges support from the MyBrainSc Scholarship, provided by the Ministry of Education, Malaysia. JS would also like to thank Antonella Palmese and Boris Leistedt for guidance on the use of the algorithms ANNz2 and Delight respectively.
